Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-04 paper/paper.qmd
Set Up the Model Equation

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{pollster}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \beta_5 \cdot \text{candidate}_i + \epsilon_i,
\end{align*}

@@

- $\beta_0$ is the expected value of PCT when all predictor variables are zero, intercept 
- $\beta_1$ captures the effect pollsters have on the response variable 
- $\beta_2$ captures the effect sample_size have on the response variable
- $\delta_k$ captures the difference in PCT between states
- $\beta_4$ captures the expected change in PCT for each additional unit increase in the end date variable 
- $\beta_5$ captures the difference in PCT associated with difference candidates

>>>>

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_2 \cdot \text{end\_date}_i + \epsilon_i,
\end{align*}

@@

- $pct_i$ is the the predicted percentage of support for Kamala Harris in each poll 
- $\beta_0$ is the intercept or expected value of PCT when all predictor variables are zero
- $\beta_1$ is the coefficient for sample size, showing the effect of the number of respondents in each poll on support
- $\delta_k$ is the coefficients representing the effect of each state
- $\beta_2$ is the coefficient for end_date, shoing how support changes over time
- $\epsilon_i$ is the error term, accounting for unexplained variability in support
